# Basic Information of MODULEs {#module}

Overview of **MODULEs**

```{r t_Md_table, echo = FALSE}
kable(df_Md_table, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

## ReferenceET {#ReferenceET}

### ReferenceET.Hargreaves {#ReferenceET.Hargreaves}

This MODULE reference to the Literature: `r Data_ReferenceET.Hargreaves$ref_title` [@`r Data_ReferenceET.Hargreaves$ref_bib`].

***InData***

```{r t_In_ReferenceET.Hargreaves, echo = FALSE}
n_In <- as.numeric(map(Data_ReferenceET.Hargreaves$InData, length))
Group_Name <- reduce(map2(names(Data_ReferenceET.Hargreaves$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_ReferenceET.Hargreaves$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_ReferenceET.Hargreaves <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_ReferenceET.Hargreaves$Param)
P_min <- as.numeric(map(Data_ReferenceET.Hargreaves$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_ReferenceET.Hargreaves$Param, function(a) a[2]))
P_unit <- as.character(map(Data_ReferenceET.Hargreaves$Param, function(a) a[3]))
P_des <- as.character(map(Data_ReferenceET.Hargreaves$Param, function(a) a[4]))
P_ReferenceET.Hargreaves <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_ReferenceET.Hargreaves$OutData, length))
Group_Name <- reduce(map2(names(Data_ReferenceET.Hargreaves$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_ReferenceET.Hargreaves$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_ReferenceET.Hargreaves <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_ReferenceET.Hargreaves, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_ReferenceET.Hargreaves, echo = FALSE}
kable(P_ReferenceET.Hargreaves, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_ReferenceET.Hargreaves, echo = FALSE}
kable(Out_ReferenceET.Hargreaves, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

### ReferenceET.Linacre {#ReferenceET.Linacre}

This MODULE reference to the Literature: `r Data_ReferenceET.Linacre$ref_title` [@`r Data_ReferenceET.Linacre$ref_bib`].

***InData***

```{r t_In_ReferenceET.Linacre, echo = FALSE}
n_In <- as.numeric(map(Data_ReferenceET.Linacre$InData, length))
Group_Name <- reduce(map2(names(Data_ReferenceET.Linacre$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_ReferenceET.Linacre$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_ReferenceET.Linacre <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_ReferenceET.Linacre$Param)
P_min <- as.numeric(map(Data_ReferenceET.Linacre$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_ReferenceET.Linacre$Param, function(a) a[2]))
P_unit <- as.character(map(Data_ReferenceET.Linacre$Param, function(a) a[3]))
P_des <- as.character(map(Data_ReferenceET.Linacre$Param, function(a) a[4]))
P_ReferenceET.Linacre <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_ReferenceET.Linacre$OutData, length))
Group_Name <- reduce(map2(names(Data_ReferenceET.Linacre$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_ReferenceET.Linacre$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_ReferenceET.Linacre <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_ReferenceET.Linacre, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_ReferenceET.Linacre, echo = FALSE}
kable(P_ReferenceET.Linacre, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_ReferenceET.Linacre, echo = FALSE}
kable(Out_ReferenceET.Linacre, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

### ReferenceET.PenMon {#ReferenceET.PenMon}

This MODULE reference to the Literature: `r Data_ReferenceET.PenMon$ref_title` [@`r Data_ReferenceET.PenMon$ref_bib`].

***InData***

```{r t_In_ReferenceET.PenMon, echo = FALSE}
n_In <- as.numeric(map(Data_ReferenceET.PenMon$InData, length))
Group_Name <- reduce(map2(names(Data_ReferenceET.PenMon$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_ReferenceET.PenMon$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_ReferenceET.PenMon <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_ReferenceET.PenMon$Param)
P_min <- as.numeric(map(Data_ReferenceET.PenMon$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_ReferenceET.PenMon$Param, function(a) a[2]))
P_unit <- as.character(map(Data_ReferenceET.PenMon$Param, function(a) a[3]))
P_des <- as.character(map(Data_ReferenceET.PenMon$Param, function(a) a[4]))
P_ReferenceET.PenMon <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_ReferenceET.PenMon$OutData, length))
Group_Name <- reduce(map2(names(Data_ReferenceET.PenMon$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_ReferenceET.PenMon$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_ReferenceET.PenMon <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_ReferenceET.PenMon, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_ReferenceET.PenMon, echo = FALSE}
kable(P_ReferenceET.PenMon, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_ReferenceET.PenMon, echo = FALSE}
kable(Out_ReferenceET.PenMon, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

## ActualET {#ActualET}

### ActualET.Gr4j {#ActualET.Gr4j}

This MODULE reference to the Literature: `r Data_ActualET.Gr4j$ref_title` [@`r Data_ActualET.Gr4j$ref_bib`].

***InData***

```{r t_In_ActualET.Gr4j, echo = FALSE}
n_In <- as.numeric(map(Data_ActualET.Gr4j$InData, length))
Group_Name <- reduce(map2(names(Data_ActualET.Gr4j$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_ActualET.Gr4j$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_ActualET.Gr4j <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_ActualET.Gr4j$Param)
P_min <- as.numeric(map(Data_ActualET.Gr4j$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_ActualET.Gr4j$Param, function(a) a[2]))
P_unit <- as.character(map(Data_ActualET.Gr4j$Param, function(a) a[3]))
P_des <- as.character(map(Data_ActualET.Gr4j$Param, function(a) a[4]))
P_ActualET.Gr4j <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_ActualET.Gr4j$OutData, length))
Group_Name <- reduce(map2(names(Data_ActualET.Gr4j$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_ActualET.Gr4j$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_ActualET.Gr4j <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_ActualET.Gr4j, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_ActualET.Gr4j, echo = FALSE}
kable(P_ActualET.Gr4j, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_ActualET.Gr4j, echo = FALSE}
kable(Out_ActualET.Gr4j, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

### ActualET.Vic {#ActualET.Vic}

This MODULE reference to the Literature: `r Data_ActualET.Vic$ref_title` [@`r Data_ActualET.Vic$ref_bib`].

***InData***

```{r t_In_ActualET.Vic, echo = FALSE}
n_In <- as.numeric(map(Data_ActualET.Vic$InData, length))
Group_Name <- reduce(map2(names(Data_ActualET.Vic$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_ActualET.Vic$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_ActualET.Vic <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_ActualET.Vic$Param)
P_min <- as.numeric(map(Data_ActualET.Vic$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_ActualET.Vic$Param, function(a) a[2]))
P_unit <- as.character(map(Data_ActualET.Vic$Param, function(a) a[3]))
P_des <- as.character(map(Data_ActualET.Vic$Param, function(a) a[4]))
P_ActualET.Vic <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_ActualET.Vic$OutData, length))
Group_Name <- reduce(map2(names(Data_ActualET.Vic$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_ActualET.Vic$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_ActualET.Vic <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_ActualET.Vic, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_ActualET.Vic, echo = FALSE}
kable(P_ActualET.Vic, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_ActualET.Vic, echo = FALSE}
kable(Out_ActualET.Vic, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

## SNOW {#SNOW}

### SNOW.17 {#SNOW.17}

This MODULE reference to the Literature: `r Data_SNOW.17$ref_title` [@`r Data_SNOW.17$ref_bib`].

***InData***

```{r t_In_SNOW.17, echo = FALSE}
n_In <- as.numeric(map(Data_SNOW.17$InData, length))
Group_Name <- reduce(map2(names(Data_SNOW.17$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_SNOW.17$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_SNOW.17 <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_SNOW.17$Param)
P_min <- as.numeric(map(Data_SNOW.17$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_SNOW.17$Param, function(a) a[2]))
P_unit <- as.character(map(Data_SNOW.17$Param, function(a) a[3]))
P_des <- as.character(map(Data_SNOW.17$Param, function(a) a[4]))
P_SNOW.17 <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_SNOW.17$OutData, length))
Group_Name <- reduce(map2(names(Data_SNOW.17$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_SNOW.17$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_SNOW.17 <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_SNOW.17, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_SNOW.17, echo = FALSE}
kable(P_SNOW.17, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_SNOW.17, echo = FALSE}
kable(Out_SNOW.17, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

### SNOW.Ddf {#SNOW.Ddf}

This MODULE reference to the Literature: `r Data_SNOW.Ddf$ref_title` [@`r Data_SNOW.Ddf$ref_bib`].

***InData***

```{r t_In_SNOW.Ddf, echo = FALSE}
n_In <- as.numeric(map(Data_SNOW.Ddf$InData, length))
Group_Name <- reduce(map2(names(Data_SNOW.Ddf$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_SNOW.Ddf$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_SNOW.Ddf <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_SNOW.Ddf$Param)
P_min <- as.numeric(map(Data_SNOW.Ddf$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_SNOW.Ddf$Param, function(a) a[2]))
P_unit <- as.character(map(Data_SNOW.Ddf$Param, function(a) a[3]))
P_des <- as.character(map(Data_SNOW.Ddf$Param, function(a) a[4]))
P_SNOW.Ddf <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_SNOW.Ddf$OutData, length))
Group_Name <- reduce(map2(names(Data_SNOW.Ddf$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_SNOW.Ddf$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_SNOW.Ddf <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_SNOW.Ddf, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_SNOW.Ddf, echo = FALSE}
kable(P_SNOW.Ddf, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_SNOW.Ddf, echo = FALSE}
kable(Out_SNOW.Ddf, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

## BASEFLOW {#BASEFLOW}

### BASEFLOW.ARNO {#BASEFLOW.ARNO}

This MODULE reference to the Literature: `r Data_BASEFLOW.ARNO$ref_title` [@`r Data_BASEFLOW.ARNO$ref_bib`].

***InData***

```{r t_In_BASEFLOW.ARNO, echo = FALSE}
n_In <- as.numeric(map(Data_BASEFLOW.ARNO$InData, length))
Group_Name <- reduce(map2(names(Data_BASEFLOW.ARNO$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_BASEFLOW.ARNO$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_BASEFLOW.ARNO <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_BASEFLOW.ARNO$Param)
P_min <- as.numeric(map(Data_BASEFLOW.ARNO$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_BASEFLOW.ARNO$Param, function(a) a[2]))
P_unit <- as.character(map(Data_BASEFLOW.ARNO$Param, function(a) a[3]))
P_des <- as.character(map(Data_BASEFLOW.ARNO$Param, function(a) a[4]))
P_BASEFLOW.ARNO <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_BASEFLOW.ARNO$OutData, length))
Group_Name <- reduce(map2(names(Data_BASEFLOW.ARNO$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_BASEFLOW.ARNO$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_BASEFLOW.ARNO <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_BASEFLOW.ARNO, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_BASEFLOW.ARNO, echo = FALSE}
kable(P_BASEFLOW.ARNO, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_BASEFLOW.ARNO, echo = FALSE}
kable(Out_BASEFLOW.ARNO, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

## INTERCEPTION {#INTERCEPTION}

### INTERCEPTION.Gash {#INTERCEPTION.Gash}

This MODULE reference to the Literature: `r Data_INTERCEPTION.Gash$ref_title` [@`r Data_INTERCEPTION.Gash$ref_bib`].

***InData***

```{r t_In_INTERCEPTION.Gash, echo = FALSE}
n_In <- as.numeric(map(Data_INTERCEPTION.Gash$InData, length))
Group_Name <- reduce(map2(names(Data_INTERCEPTION.Gash$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_INTERCEPTION.Gash$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_INTERCEPTION.Gash <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_INTERCEPTION.Gash$Param)
P_min <- as.numeric(map(Data_INTERCEPTION.Gash$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_INTERCEPTION.Gash$Param, function(a) a[2]))
P_unit <- as.character(map(Data_INTERCEPTION.Gash$Param, function(a) a[3]))
P_des <- as.character(map(Data_INTERCEPTION.Gash$Param, function(a) a[4]))
P_INTERCEPTION.Gash <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_INTERCEPTION.Gash$OutData, length))
Group_Name <- reduce(map2(names(Data_INTERCEPTION.Gash$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_INTERCEPTION.Gash$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_INTERCEPTION.Gash <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_INTERCEPTION.Gash, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_INTERCEPTION.Gash, echo = FALSE}
kable(P_INTERCEPTION.Gash, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_INTERCEPTION.Gash, echo = FALSE}
kable(Out_INTERCEPTION.Gash, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

## InfiltratRat {#InfiltratRat}

### InfiltratRat.GreenAmpt {#InfiltratRat.GreenAmpt}

This MODULE reference to the Literature: `r Data_InfiltratRat.GreenAmpt$ref_title` [@`r Data_InfiltratRat.GreenAmpt$ref_bib`].

***InData***

```{r t_In_InfiltratRat.GreenAmpt, echo = FALSE}
n_In <- as.numeric(map(Data_InfiltratRat.GreenAmpt$InData, length))
Group_Name <- reduce(map2(names(Data_InfiltratRat.GreenAmpt$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_InfiltratRat.GreenAmpt$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_InfiltratRat.GreenAmpt <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_InfiltratRat.GreenAmpt$Param)
P_min <- as.numeric(map(Data_InfiltratRat.GreenAmpt$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_InfiltratRat.GreenAmpt$Param, function(a) a[2]))
P_unit <- as.character(map(Data_InfiltratRat.GreenAmpt$Param, function(a) a[3]))
P_des <- as.character(map(Data_InfiltratRat.GreenAmpt$Param, function(a) a[4]))
P_InfiltratRat.GreenAmpt <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_InfiltratRat.GreenAmpt$OutData, length))
Group_Name <- reduce(map2(names(Data_InfiltratRat.GreenAmpt$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_InfiltratRat.GreenAmpt$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_InfiltratRat.GreenAmpt <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_InfiltratRat.GreenAmpt, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_InfiltratRat.GreenAmpt, echo = FALSE}
kable(P_InfiltratRat.GreenAmpt, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_InfiltratRat.GreenAmpt, echo = FALSE}
kable(Out_InfiltratRat.GreenAmpt, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

## Infiltration {#Infiltration}

### Infiltration.OIER {#Infiltration.OIER}

This MODULE reference to the Literature: `r Data_Infiltration.OIER$ref_title` [@`r Data_Infiltration.OIER$ref_bib`].

***InData***

```{r t_In_Infiltration.OIER, echo = FALSE}
n_In <- as.numeric(map(Data_Infiltration.OIER$InData, length))
Group_Name <- reduce(map2(names(Data_Infiltration.OIER$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_Infiltration.OIER$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_Infiltration.OIER <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_Infiltration.OIER$Param)
P_min <- as.numeric(map(Data_Infiltration.OIER$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_Infiltration.OIER$Param, function(a) a[2]))
P_unit <- as.character(map(Data_Infiltration.OIER$Param, function(a) a[3]))
P_des <- as.character(map(Data_Infiltration.OIER$Param, function(a) a[4]))
P_Infiltration.OIER <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_Infiltration.OIER$OutData, length))
Group_Name <- reduce(map2(names(Data_Infiltration.OIER$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_Infiltration.OIER$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_Infiltration.OIER <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_Infiltration.OIER, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_Infiltration.OIER, echo = FALSE}
kable(P_Infiltration.OIER, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_Infiltration.OIER, echo = FALSE}
kable(Out_Infiltration.OIER, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

### Infiltration.SER {#Infiltration.SER}

This MODULE reference to the Literature: `r Data_Infiltration.SER$ref_title` [@`r Data_Infiltration.SER$ref_bib`].

***InData***

```{r t_In_Infiltration.SER, echo = FALSE}
n_In <- as.numeric(map(Data_Infiltration.SER$InData, length))
Group_Name <- reduce(map2(names(Data_Infiltration.SER$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_Infiltration.SER$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_Infiltration.SER <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_Infiltration.SER$Param)
P_min <- as.numeric(map(Data_Infiltration.SER$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_Infiltration.SER$Param, function(a) a[2]))
P_unit <- as.character(map(Data_Infiltration.SER$Param, function(a) a[3]))
P_des <- as.character(map(Data_Infiltration.SER$Param, function(a) a[4]))
P_Infiltration.SER <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_Infiltration.SER$OutData, length))
Group_Name <- reduce(map2(names(Data_Infiltration.SER$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_Infiltration.SER$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_Infiltration.SER <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_Infiltration.SER, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_Infiltration.SER, echo = FALSE}
kable(P_Infiltration.SER, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_Infiltration.SER, echo = FALSE}
kable(Out_Infiltration.SER, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

## RUNOFF {#RUNOFF}

### RUNOFF.Gr4j {#RUNOFF.Gr4j}

This MODULE reference to the Literature: `r Data_RUNOFF.Gr4j$ref_title` [@`r Data_RUNOFF.Gr4j$ref_bib`].

***InData***

```{r t_In_RUNOFF.Gr4j, echo = FALSE}
n_In <- as.numeric(map(Data_RUNOFF.Gr4j$InData, length))
Group_Name <- reduce(map2(names(Data_RUNOFF.Gr4j$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_RUNOFF.Gr4j$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_RUNOFF.Gr4j <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_RUNOFF.Gr4j$Param)
P_min <- as.numeric(map(Data_RUNOFF.Gr4j$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_RUNOFF.Gr4j$Param, function(a) a[2]))
P_unit <- as.character(map(Data_RUNOFF.Gr4j$Param, function(a) a[3]))
P_des <- as.character(map(Data_RUNOFF.Gr4j$Param, function(a) a[4]))
P_RUNOFF.Gr4j <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_RUNOFF.Gr4j$OutData, length))
Group_Name <- reduce(map2(names(Data_RUNOFF.Gr4j$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_RUNOFF.Gr4j$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_RUNOFF.Gr4j <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_RUNOFF.Gr4j, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_RUNOFF.Gr4j, echo = FALSE}
kable(P_RUNOFF.Gr4j, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_RUNOFF.Gr4j, echo = FALSE}
kable(Out_RUNOFF.Gr4j, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

### RUNOFF.OIER {#RUNOFF.OIER}

This MODULE reference to the Literature: `r Data_RUNOFF.OIER$ref_title` [@`r Data_RUNOFF.OIER$ref_bib`].

***InData***

```{r t_In_RUNOFF.OIER, echo = FALSE}
n_In <- as.numeric(map(Data_RUNOFF.OIER$InData, length))
Group_Name <- reduce(map2(names(Data_RUNOFF.OIER$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_RUNOFF.OIER$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_RUNOFF.OIER <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_RUNOFF.OIER$Param)
P_min <- as.numeric(map(Data_RUNOFF.OIER$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_RUNOFF.OIER$Param, function(a) a[2]))
P_unit <- as.character(map(Data_RUNOFF.OIER$Param, function(a) a[3]))
P_des <- as.character(map(Data_RUNOFF.OIER$Param, function(a) a[4]))
P_RUNOFF.OIER <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_RUNOFF.OIER$OutData, length))
Group_Name <- reduce(map2(names(Data_RUNOFF.OIER$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_RUNOFF.OIER$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_RUNOFF.OIER <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_RUNOFF.OIER, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_RUNOFF.OIER, echo = FALSE}
kable(P_RUNOFF.OIER, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_RUNOFF.OIER, echo = FALSE}
kable(Out_RUNOFF.OIER, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

### RUNOFF.SER {#RUNOFF.SER}

This MODULE reference to the Literature: `r Data_RUNOFF.SER$ref_title` [@`r Data_RUNOFF.SER$ref_bib`].

***InData***

```{r t_In_RUNOFF.SER, echo = FALSE}
n_In <- as.numeric(map(Data_RUNOFF.SER$InData, length))
Group_Name <- reduce(map2(names(Data_RUNOFF.SER$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_RUNOFF.SER$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_RUNOFF.SER <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_RUNOFF.SER$Param)
P_min <- as.numeric(map(Data_RUNOFF.SER$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_RUNOFF.SER$Param, function(a) a[2]))
P_unit <- as.character(map(Data_RUNOFF.SER$Param, function(a) a[3]))
P_des <- as.character(map(Data_RUNOFF.SER$Param, function(a) a[4]))
P_RUNOFF.SER <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_RUNOFF.SER$OutData, length))
Group_Name <- reduce(map2(names(Data_RUNOFF.SER$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_RUNOFF.SER$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_RUNOFF.SER <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_RUNOFF.SER, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_RUNOFF.SER, echo = FALSE}
kable(P_RUNOFF.SER, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_RUNOFF.SER, echo = FALSE}
kable(Out_RUNOFF.SER, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

### RUNOFF.Vic {#RUNOFF.Vic}

This MODULE reference to the Literature: `r Data_RUNOFF.Vic$ref_title` [@`r Data_RUNOFF.Vic$ref_bib`].

***InData***

```{r t_In_RUNOFF.Vic, echo = FALSE}
n_In <- as.numeric(map(Data_RUNOFF.Vic$InData, length))
Group_Name <- reduce(map2(names(Data_RUNOFF.Vic$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_RUNOFF.Vic$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_RUNOFF.Vic <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_RUNOFF.Vic$Param)
P_min <- as.numeric(map(Data_RUNOFF.Vic$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_RUNOFF.Vic$Param, function(a) a[2]))
P_unit <- as.character(map(Data_RUNOFF.Vic$Param, function(a) a[3]))
P_des <- as.character(map(Data_RUNOFF.Vic$Param, function(a) a[4]))
P_RUNOFF.Vic <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_RUNOFF.Vic$OutData, length))
Group_Name <- reduce(map2(names(Data_RUNOFF.Vic$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_RUNOFF.Vic$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_RUNOFF.Vic <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_RUNOFF.Vic, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_RUNOFF.Vic, echo = FALSE}
kable(P_RUNOFF.Vic, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_RUNOFF.Vic, echo = FALSE}
kable(Out_RUNOFF.Vic, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

### RUNOFF.VM {#RUNOFF.VM}

This MODULE reference to the Literature: `r Data_RUNOFF.VM$ref_title` [@`r Data_RUNOFF.VM$ref_bib`].

***InData***

```{r t_In_RUNOFF.VM, echo = FALSE}
n_In <- as.numeric(map(Data_RUNOFF.VM$InData, length))
Group_Name <- reduce(map2(names(Data_RUNOFF.VM$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_RUNOFF.VM$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_RUNOFF.VM <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_RUNOFF.VM$Param)
P_min <- as.numeric(map(Data_RUNOFF.VM$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_RUNOFF.VM$Param, function(a) a[2]))
P_unit <- as.character(map(Data_RUNOFF.VM$Param, function(a) a[3]))
P_des <- as.character(map(Data_RUNOFF.VM$Param, function(a) a[4]))
P_RUNOFF.VM <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_RUNOFF.VM$OutData, length))
Group_Name <- reduce(map2(names(Data_RUNOFF.VM$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_RUNOFF.VM$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_RUNOFF.VM <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_RUNOFF.VM, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_RUNOFF.VM, echo = FALSE}
kable(P_RUNOFF.VM, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_RUNOFF.VM, echo = FALSE}
kable(Out_RUNOFF.VM, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

## GROUNDWATER {#GROUNDWATER}

### GROUNDWATER.Vic {#GROUNDWATER.Vic}

This MODULE reference to the Literature: `r Data_GROUNDWATER.Vic$ref_title` [@`r Data_GROUNDWATER.Vic$ref_bib`].

***InData***

```{r t_In_GROUNDWATER.Vic, echo = FALSE}
n_In <- as.numeric(map(Data_GROUNDWATER.Vic$InData, length))
Group_Name <- reduce(map2(names(Data_GROUNDWATER.Vic$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_GROUNDWATER.Vic$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_GROUNDWATER.Vic <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_GROUNDWATER.Vic$Param)
P_min <- as.numeric(map(Data_GROUNDWATER.Vic$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_GROUNDWATER.Vic$Param, function(a) a[2]))
P_unit <- as.character(map(Data_GROUNDWATER.Vic$Param, function(a) a[3]))
P_des <- as.character(map(Data_GROUNDWATER.Vic$Param, function(a) a[4]))
P_GROUNDWATER.Vic <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_GROUNDWATER.Vic$OutData, length))
Group_Name <- reduce(map2(names(Data_GROUNDWATER.Vic$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_GROUNDWATER.Vic$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_GROUNDWATER.Vic <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_GROUNDWATER.Vic, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_GROUNDWATER.Vic, echo = FALSE}
kable(P_GROUNDWATER.Vic, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_GROUNDWATER.Vic, echo = FALSE}
kable(Out_GROUNDWATER.Vic, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

## ROUTE {#ROUTE}

### ROUTE.G2RES {#ROUTE.G2RES}

This MODULE reference to the Literature: `r Data_ROUTE.G2RES$ref_title` [@`r Data_ROUTE.G2RES$ref_bib`].

***InData***

```{r t_In_ROUTE.G2RES, echo = FALSE}
n_In <- as.numeric(map(Data_ROUTE.G2RES$InData, length))
Group_Name <- reduce(map2(names(Data_ROUTE.G2RES$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_ROUTE.G2RES$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_ROUTE.G2RES <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_ROUTE.G2RES$Param)
P_min <- as.numeric(map(Data_ROUTE.G2RES$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_ROUTE.G2RES$Param, function(a) a[2]))
P_unit <- as.character(map(Data_ROUTE.G2RES$Param, function(a) a[3]))
P_des <- as.character(map(Data_ROUTE.G2RES$Param, function(a) a[4]))
P_ROUTE.G2RES <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_ROUTE.G2RES$OutData, length))
Group_Name <- reduce(map2(names(Data_ROUTE.G2RES$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_ROUTE.G2RES$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_ROUTE.G2RES <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_ROUTE.G2RES, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_ROUTE.G2RES, echo = FALSE}
kable(P_ROUTE.G2RES, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_ROUTE.G2RES, echo = FALSE}
kable(Out_ROUTE.G2RES, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

### ROUTE.Gr4j {#ROUTE.Gr4j}

This MODULE reference to the Literature: `r Data_ROUTE.Gr4j$ref_title` [@`r Data_ROUTE.Gr4j$ref_bib`].

***InData***

```{r t_In_ROUTE.Gr4j, echo = FALSE}
n_In <- as.numeric(map(Data_ROUTE.Gr4j$InData, length))
Group_Name <- reduce(map2(names(Data_ROUTE.Gr4j$InData), n_In, rep), c)
Variable_Name <- reduce(map(Data_ROUTE.Gr4j$InData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
In_ROUTE.Gr4j <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
P_Name <- names(Data_ROUTE.Gr4j$Param)
P_min <- as.numeric(map(Data_ROUTE.Gr4j$Param, function(a) a[1]))
P_max <- as.numeric(map(Data_ROUTE.Gr4j$Param, function(a) a[2]))
P_unit <- as.character(map(Data_ROUTE.Gr4j$Param, function(a) a[3]))
P_des <- as.character(map(Data_ROUTE.Gr4j$Param, function(a) a[4]))
P_ROUTE.Gr4j <- data.frame(Paramter = P_Name, Min = P_min, Max = P_max, Unit = P_unit, Description = P_des)
n_Out <- as.numeric(map(Data_ROUTE.Gr4j$OutData, length))
Group_Name <- reduce(map2(names(Data_ROUTE.Gr4j$OutData), n_Out, rep), c)
Variable_Name <- reduce(map(Data_ROUTE.Gr4j$OutData, names), c)
Unit_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Unit_dataset[[a]][[b]]))
Des_ <- as.character(map2(Group_Name, Variable_Name, function(a, b) Des_dataset[[a]][[b]]))
Out_ROUTE.Gr4j <- data.frame(Group = Group_Name, Variable = Variable_Name, Unit = Unit_, Description = Des_)
kable(In_ROUTE.Gr4j, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***Param***

```{r t_P_ROUTE.Gr4j, echo = FALSE}
kable(P_ROUTE.Gr4j, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

***OutData***

```{r t_Out_ROUTE.Gr4j, echo = FALSE}
kable(Out_ROUTE.Gr4j, row.names = F) %>% collapse_rows(1) %>% kable_styling(latex_options = "hold_position")
```

Return to the [Overview](#module) of MODULEs.

